Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-05-10 src/tex/ms.tex
Add Zhu's constraint to table
Minor wording
no floatfix for arxiv

\documentclass[aps,prd,twocolumn,superscriptaddress,preprintnumbers,floatfix,nofootinbib]{revtex4-2}

@@

\begin{table}
    \caption{
        Comparison of our constraints to \citet{Okounkova_2022} and \citet{Wang_2021}.
        CL is the credible level.
    }
    \begin{ruledtabular}
        \variable{output/comparison_summary.txt}
    \end{ruledtabular}
    \label{tab:comparison_summary}
\end{table}

>>>>

\documentclass[aps,prd,twocolumn,superscriptaddress,preprintnumbers,nofootinbib]{revtex4-2}

@@

\begin{table}
    \caption{
        Comparison of our constraints with previous studies.
        CL is the credible level.
    }
    \begin{ruledtabular}
        \variable{output/comparison_summary.txt}
    \end{ruledtabular}
    \label{tab:comparison_summary}
\end{table}
